---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
h2 {color: #b603fc}

```

## Types of Content Recommended by Instagram

This dynamic report showcases my findings through my observational logging of the types of content recommended to me on my **Instagram** feed. I kept track of the **most commonly recommended** categories of posts and **how often** they showed up!

```{r}
library(tidyverse)

#Load dataset
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQ9boQpLDHDq1YCRuEGHy9ZEcp4OE6-CgbRvjk-BJb5wYNVWooXHQtZ4snHSrBNwZ5lzbMQjRdXEnKL/pub?output=csv")

#Rename categories
latest_data <- rename(logged_data,
                      timestamp = 1,
                      content_type = 2,
                      content_number = 3,
                      happiness = 4)

#First summary value: mean happiness
mean_happiness <- mean(latest_data$happiness)

#Second summary value: minimum number of most common posts
min_posts <- min(latest_data$content_number)

#First bar chart: counts of different types of content
latest_data %>%
  ggplot() +
  geom_bar(aes(x = content_type, fill = timestamp)) +
  labs(title = "Most common types of content per day",
       subtitle = "The most common forms of content recommended by Instagram,
       sorted by day!",
       caption = "by Zaid",
       x = "Type of content",
       y = "Count of 'most common' appearances")

#Second bar chart: counts of different levels of happiness with content
latest_data %>%
  ggplot() +
  geom_bar(aes(x = happiness, fill = timestamp)) +
  labs(title = "Happiness with recommendations by day",
       subtitle = "How satisfied Instagram's recommendations made me.",
       caption = "by Zaid",
       x = "Happiness",
       y = "Count")
```

Here are a few extra points of interest about the data above:

-   The average level of happiness was `r round(mean_happiness, 1)`
-   The minimum number of "most common" posts was `r min_posts`
